When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-02-27 presentation/inbreeding.Rmd
Annoying errors in compiling

@@

```{r echo = FALSE, fig.height = 4, fig.width = 5}
inputPanel(
  sliderInput("rr", label = "Relatedness", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  sliderInput("dd", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.1)
)
par(bg = 'transparent', mar = c(0.5, 0.5, 0.5, 0.5));
plot(x = 1:10, y = 1:10, xaxt = "n", yaxt = "n", xlab = "", ylab = "");
# Add see-saw function here to animate the balance
```

@@

@@

```{r lmSim, fig.show='animate', echo = FALSE}
inputPanel(
  sliderInput("Imm", label = "Immigrants", width="100%",
              min = 0.0, max = 10, value = 0, step = 1), 
  sliderInput("ID", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 10, value = 0, step = 0.5), 
  sliderInput("cost", label = "Strategy Cost", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  sliderInput("mu", label = "Mutation Rate", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  actionButton("mate", "New Generation"),
  actionButton("reset", "Reset")
)

@@

@@

```{r lmSim3, fig.show='animate', echo = FALSE}
inputPanel(
  sliderInput("Imm3", label = "Immigrants", width="100%",
              min = 0.0, max = 10, value = 0, step = 1), 
  sliderInput("ID3", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 10, value = 0, step = 0.5), 
  sliderInput("cost3", label = "Strategy Cost", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  sliderInput("mu3", label = "Mutation Rate", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  actionButton("mate3", "New Generation"),
  actionButton("reset3", "Reset")
)

@@

```{r lmSim2, fig.show='animate', echo = FALSE}
inputPanel(
  sliderInput("Imm2", label = "Immigrants", width="100%",
              min = 0.0, max = 10, value = 2, step = 1), 
  sliderInput("ID2", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 10, value = 8, step = 0.5), 
  sliderInput("cost2", label = "Strategy Cost", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  sliderInput("mu2", label = "Mutation Rate", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  actionButton("mate2", "New Generation"),
  actionButton("reset2", "Reset")
)

>>>>

<!---

## Inbeeding theory

@@

```{r echo = FALSE}
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
inputPanel(
  sliderInput("rr", label = "Relatedness", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  sliderInput("dd", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.1)
)
renderPlot({
    par(bg = 'transparent', mar = c(0.5, 0.5, 0.5, 0.5));
    plot(x = -1:1, y = -1:1, xaxt = "n", yaxt = "n", xlab = "", ylab = "Fitness", 
         type = "n", xlim = c(-1, 1), ylim = c(-1, 1), bty = "n");
    points(x = 0, y = 0, cex = 5, pch = 20, col = "black");
    val <- seq(from = (-1 * pi)/4, to = (1 * pi)/4, length = 1000);
    hx  <- cos(val);
    hy  <- sin(val);
    fva <- seq(from = 0, to = 1, length = 1000);
    fit <- 0.5*(1 + input$rr)*(1 - input$dd);
    sqd <- (fva - fit)*(fva - fit);
    clf <- which(sqd == min(sqd));
    fx  <- cos(val[clf]);
    fy  <- sin(val[clf]);
    points(x = hx, y = hy, lwd = 2, type = "l");
    points(x = seq(from = 0, to = 1, length = 100), y = rep(0, 100), 
           type = "l", lty = "dotted", col = "red");
    ia_box <- mbox(x0 = -1.1, x1 = -0.1, y0 = -0.9, y1 = -1.1);
    polygon(x=ia_box$x, y=ia_box$y, lwd=3, border="black", col="black");
    ip_box <- mbox(x0 = 0.1, x1 = 1.1, y0 = -0.9, y1 = -1.1);
    polygon(x=ip_box$x, y=ip_box$y, lwd=3, border="black", col="black");
    points(x = seq(from = -1, to = 1, length = 100), y = rep(-0.85, 100), 
           lwd = 6, type = "l");
    points(x = rep(0, 100), y = seq(from = -0.85, to = 0, length = 100), 
           lwd = 6, type = "l");
    text(x = -0.6, y = -1, labels = "Avoid inbreeding", cex = 1.75, col = "red");
    text(x = 0.6, y = -1, labels = "Inbreeding", cex = 1.75, col = "white");
    text(x = 0.8, y = 0.75, labels = "n", cex = 3);
    text(x = 0.8, y = -0.75, labels = "0", cex = 3);
    text(x = -1, y = 0, labels = expression(frac(n,2)), cex = 3);
    points(x = 0, y = 0, cex = 3, pch = 20, col = "red");
    arrows(x0 = 0, x1 = fx, y0 = 0, y1 = fy, lwd = 3, col = "black");
    arrows(x0 = 0, x1 = -0.9, y0 = 0, y1 = 0, lwd = 3, col = "red");
})
```

@@

--->

@@

```{r IBM_1, fig.show='animate', echo = FALSE}
inputPanel(
  sliderInput("Imm", label = "Immigrants", width="100%",
              min = 0.0, max = 10, value = 0, step = 1), 
  sliderInput("ID", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 10, value = 0, step = 0.5), 
  sliderInput("cost", label = "Strategy Cost", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  sliderInput("mu", label = "Mutation Rate", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  actionButton("mate", "New Generation"),
  actionButton("reset", "Reset")
)

@@

## Again

@@

```{r IBM_3, fig.show = 'animate', echo = FALSE}
inputPanel(
  sliderInput("Imm3", label = "Immigrants", width="100%",
              min = 0.0, max = 10, value = 0, step = 1), 
  sliderInput("ID3", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 10, value = 0, step = 0.5), 
  sliderInput("cost3", label = "Strategy Cost", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  sliderInput("mu3", label = "Mutation Rate", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  actionButton("mate3", "New Generation"),
  actionButton("reset3", "Reset")
)

@@

```{r IBM_2, fig.show = 'animate', echo = FALSE}
inputPanel(
  sliderInput("Imm2", label = "Immigrants", width="100%",
              min = 0.0, max = 10, value = 2, step = 1), 
  sliderInput("ID2", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 10, value = 8, step = 0.5), 
  sliderInput("cost2", label = "Strategy Cost", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  sliderInput("mu2", label = "Mutation Rate", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  actionButton("mate2", "New Generation"),
  actionButton("reset2", "Reset")
)
